{$\ch_2(\tf)$ Optimality Conditions for a Finite-time Horizon\thanksref{mytitlenote}}

### 2019-09-02 Final Submission/FH Optimality Conditions PaperArxiv.tex
final version
The folder named "Final Submission" contains the final version of the paper

%\documentclass[preprint]{elsarticle}
\documentclass[twocolumn]{autart}  
\input{paperPreamble}

@@

\end{frontmatter}
%Introduction
%Introduction
\section{Introduction}
%Simulation, design, and control of dynamical systems play an important role in numerous scientific and industrial tasks such as signal propagation in the nervous system\cite{kellems2009low}, heat dissipation, prediction of major weather events \cite{BoyP11,Sha03,Ant05}. 
Simulation, design, and control of dynamical systems play an important role in numerous scientific and industrial tasks such as \textcolor{blue}{signal propagation in the nervous system\cite{kellems2009low};  the synthesis  of
interconnect \cite{BonD07} and semiconductor devices \cite{Hess2014}; large-scale inverse problem,
 \cite{Druskin2011solution,Lieberman2010,de2015nonlinear}; and prediction of major weather events \cite{Ant05}.}
The need for  detailed  models due to the increasing demand for greater resolution leads to  
large-scale dynamical systems, posing tremendous computational difficulties when applied in numerical simulations. In order to overcome these challenges, we perform  model reduction where we replace the large-scale dynamics with high-fidelity reduced representations.

@@

\textcolor{blue}{In this paper,  we explore optimal model reduction over a finite time horizon. We use a time-limited version of the $\ch_2$ norm, denoted by $\ch_2(\tf)$, to quantify the model reduction error.}
 Optimality requires a parametrization of the reduced model. We will work with the time-domain representation of the dynamical system to derive the optimality conditions. Specifically, we represent the impulse response of the reduced dynamical system using the modal decomposition, i.e.,
 \begin{equation}\label{kernel}
\begin{aligned}
\h_r(t)=\C_r e^{\A_r t}\B_r=\sum_{i=1}^r e^{\lambda_it}\lc_i\rc_i^T.
\end{aligned}
\end{equation}
where $\lambda_i$'s are the eigenvalues of $\A_r$, and $\lc_i \in \CC^{p\times 1}, \rc_i\in \CC^{m\times1}$. 
In other words, the impulse response is expressed as a sum of $r$ rank-1 $p\times m$  matrices.
To simplify the presentation,  we assume  that $\lambda_i$'s, the reduced order poles,  are simple.  The representation \eqref{kernel} 
is nothing but a state-space transformation on $\h_r(t)=\C_r e^{\A_r t}\B_r$ using the eigenvectors of $\A_r$. 
Using the parametrization of the reduced model in \eqref{kernel}, we derive interpolatory optimality conditions in the $\ch_2(\tf)$ norm and implement a model reduction algorithm that satisfies these optimality conditions.

\textcolor{blue}{The advantage of the interpolation framework we will develop  is that 
we do not require the reduced-model to be obtained via projection, as usually assumed in model reduction \cite{Ant05}. Indeed, one observation we will make is that unlike in the infinite-horizon $\ch_2$ approximation problem, the optimal reduced model in the finite-horizon norm is not necessarily given by a projection and thus a projection-based approach will not be able to satisfy the optimality conditions. Therefore,  
by treating the poles and residues in \eqref{kernel} as the parameters and directly working with them, we  obtain a reduced model to satisfy the optimality conditions exactly.}

@@

%Interpolatory Model Reduction
\subsection{Interpolatory Conditions for Optimal $\ch_2$ Model Reduction}
Given a reduced order $r$, the goal is to construct a reduced order model whose transfer function $\HH_r(s)$ minimizes the $\ch_2$ error norm $\norm{\HH - \HH_r}_{\ch_2}$.  Since this is a non-convex optimization problem, the usual, numerically feasible, approach  is to find a reduced model that satisfies the necessary conditions for $\ch_2$ optimality. These conditions can be formulated in terms of Sylvester equations \cite{Wil70,HylB85} or interpolation \cite{MeiL67,GugBA08}. These two frameworks are equivalent \cite{GugBA08}. In this paper, we will focus on the interpolation framework.
\begin{theorem} \label{h2thm}%{\text{\cite {MeiL67, GugBA08}}}
Let 
$$
\h_r(t)=\sum_{k=1}^r e^{\lambda_kt}\lc_k\rc_k^T \qquad \Longleftrightarrow \qquad \HH_r(s) = \sum_{k=1}^r \frac{\lc_k\rc_k^T}{s-\lambda_k}
$$
be the best $r^{th}$ order approximation of an asymptotically stable linear dynamical system  $\HH(s)$ with respect to the $\ch_2$ norm. Then, for $k=1, 2, ... , r$,
\begin{equation} \label{eqn:h2cond}
\begin{aligned}
\lc_k^T\HH(-\lambda_k)&=\lc_k^T\HH_r(-\lambda_k),\\~~
\HH(-\lambda_k)\rc_k&=\HH_r(-\lambda_k)\rc_k,\\
\lc_k^T\HH'(-\lambda_k)\rc_k&=\lc_k^T\HH_r'(-\lambda_k)\rc_k.
\end{aligned}
\end{equation}
\end{theorem}
{\color{blue} where $\HH'(s)$ denotes the derivative of $\HH(s)$ with respect to $s$.}
{\color{blue}For more details on Theorem \ref{h2thm}, see {\cite {GugBA08,AntBG10b}}.}
This result states that the transfer function of the optimal $\ch_2$ approximation to $\HH(s)$ is a (tangential) Hermite interpolant where the interpolation points are the mirror images of the reduced-order poles $\{\lambda_k\}$, and the tangental directions are given by the corresponding residues $\{\lc_k\rc_k^T\}$.  Since the optimality conditions depend on the reduced-model to be computed, the solution requires a nonlinear iteration. The Iterative Rational Krylov Algorithm (IRKA)  \cite{GugBA08} and its variants such as \cite{beattie2012realization,gerstner2007hom,CasL18,beattie2009trust} use these interpolation based optimality conditions to produce   an interpolatory, locally $\ch_2$ optimal reduced model. The next section will extend this framework to the finite-time interval case.

%FH model reduction
\section{$\ch_2(\tf)$ Optimal Model Reduction on a Finite Horizon}  \label{sec:main} 
%If we are interested  in the behavior of a system only in a finite time interval (or access to a numerical simulation only on a finite time interval), we can obtain better reduced models by defining the measure of approximation quality over the interval of interest, instead of  focussing on the infinite time horizon. 
%
{\color{blue}
In this section, we present  the main theoretical results of the paper i.e., the interpolatory $\ch_2(\tf)$  optimality conditions, and discuss their implications.}

@@

%Error measures in a finite-time horizon
\subsection{$\ch_2(t_f)$ Norm on a Finite-time Horizon}
It is immediately clear from the time-domain definition of the (infinite-horizon) $\ch_2$ norm how to define the finite-horizon version:
\begin{Definition}\label{innerh2}
Let $\h(t)$ and $\g(t)$ denote the impulse responses of two dynamical systems with real state-space realizations.  
For a finite-time horizon 
$[0,t_f]$, the $\ch_2(\tf)$\footnote{\textcolor{blue}{Even though we are using an error measure specifically formulated in the time domain,   following \cite{RedK17,GoyR17} we choose to use  the $\ch_2(\tf)$ notation, despite the term $\ch_2$  is mostly associated with a measure defined in the frequency domain. Our main reason is to keep the connection to the infinite horizon problem where the measure in the frequency- and time-domains are equivalent. And more importantly, as in the regular $\ch_2$ case, the optimality conditions will still appear as interpolation conditions in the frequency domain. 
 %In the Since the time domain and frequency domain functions are equivalent,  this notation is appropriate. Furthermore, since the infinite horizon, and finite horizon case appear to be connected, the notation $\mathcal{H}_2(t_f)$ illustrates this connection. \cite{RedK17,GoyR17} use similar notation.
 }}
   inner product $\langle \cdot, \cdot \rangle_{\ch_2(\tf)}$ 
and $\ch_2(\tf)$ norm $\norm{\cdot}_{\ch_2(\tf)}$ are defined as  
\begin{align*}
\langle \h, \g \rangle_{\ch_2(\tf)} &=\int_0^{\tf} \mathsf{Tr}( (\h(t))^T \g(t)) dt, \\%\quad \mbox{and}\quad
\norm{\h}_{\ch_2(\tf)} &=\sqrt{\int_0^{\tf} \norm{\h(t)}_F^2 dt}.
\end{align*}

@@

{\color{blue}

@@

%\begin{dmath}\label{eqn:l1} 
%\pder[\J]{\lambda_k} =-2\lc_k^T \left(\sum_{j=1}^n \cc_j\bb_j^T \dfrac{({\tf}(\lambda_k+\rho_j)-1)e^{(\rho_j+\lambda_k){\tf}}+1}{(\lambda_k+\rho_j)^2}\right)\rc_k  
%+2\lc_k^T \left(\sum^r_{i=1} \lc_i\rc_i^T\dfrac{({\tf}(\lambda_i+\lambda_j\k)-1)e^{(\lambda_i+\lambda_k){\tf}}+1}{(\lambda_i+\lambda_k)^2}\right)\rc_k.
%\end{dmath}
%\end{aligned}
%\end{equation}
Lemma \eqref{mgexp}, specifically \eqref{eqn:Gpatlk} and \eqref{eqn:Grpatlk}, show that the expressions in the parentheses in \eqref{eqn:l11}  and \eqref{eqn:l12}   are, respectively, $-\G'(-\lambda_k)$ and $-\G_r'(-\lambda_k)$.
If $\pder[\J]{\lambda_k}= 0$, then
\begin{align*}
\lc_k^T\G'(-\lambda_k)\rc_k&=\lc_k^T\G_r'(-\lambda_k)\rc_k,
\end{align*}
which completes the proof.
\begin{flushright} $\Box$  \end{flushright}
{\color{blue} We note that the interval of interest is problem dependent and the choice of the interval, i.e., the choice of $t_f$, may depend on the model. However, these optimality conditions hold for any choice of $t_f>0$.}

%Remark
\begin{remark}
{\color{blue} In the infinite-horizon case, if  $\HH_r(s)$ is the best $\ch_2$ approximation to $\HH(s)$, then $\HH_r(s)$ interpolates $\HH(s)$. However, in the finite-horizon case, 
the interpolant is $\G_r(s)$, and the interpolated function is $\G(s)$; thus $\HH_r(s)$ does not interpolate $\HH(s)$. To give more intuition about these resulting interpolation conditions, considere the time-limited function $\g(t)$ such that 
$\g(t)=\h(t)$ when   $t\leq {\tf}$ and $\g(t)=0$ when when $t > {\tf}$.
%\begin{align*}
%\g(t)=
% \begin{cases} 
%      \h(t) &    t\leq {\tf}, \\    
%      0 &    t > {\tf}.
%   \end{cases}
%\end{align*}
A direct calculation shows that $\G(s)$ is the Laplace transformation of $\g(t)$. Similarly let $\g_r(t)$ 
denote the time-limited version of $\h_r(t)$. Then its Laplace transformation is 
 $\G_r(s)$.  Therefore, the optimality conditions  \eqref{eqn:cond1}--\eqref{eqn:cond3}
 correspond to optimal interpolation of $\G(s)$ (Laplace transform of a time-limited function)
 by $\G_r(s)$, (Laplace transform of another time limited function.) The fact that  
 $\g(t)$ and   $\g_r(t)$ are both time-limited is the precise reason  why we cannot simply apply $\ch_2$ optimal reduction  to $\G(s)$. The method of \cite{beattie2012realization}, called TF-IRKA, does not require the original function to be a rational function. Thus, in principle we can use TF-IRKA to reduce $\G(s)$. However, the resulting reduced model is a rational function without any structure. In our case, the reduced model $\G_r(s)$ needs to retain the same structure as $\G(s)$ so that we can extract an $\HH_r(s)$. In other words, if we simply apply an $\ch_2$ optimal algorithm to $\G(s)$, we would be approximating a finite horizon model by an infinite horizon one and we cannot extract $\HH_r(s)$. Therefore, a new  algorithmic framework  is needed as we discuss in more detail in Section \ref{sec:discuss}.}
\end{remark}

\begin{remark}
{\color{blue}
For an unstable dynamical system without any purely imaginary eigenvalues, one can work with the
 $\mathcal{L}_2$ norm by decomposing it into a stable and anti-stable system, and then obtain an interpolatory reduced model based on this measure.  However, this solution requires destroying the causality of the underlying dynamics \cite{magruder2010rational}. This is not the framework we are interested in here and we  work with a finite-time interval. }
 \end{remark}

%%remark
%\begin{remark}
%{\color{blue} In the infinite-horizon case, if $\HH_r(s)$ is the best $\ch_2$ approximation to $\HH(s)$, then $\HH_r(s)$ interpolates $\HH(s)$. However, in the finite-horizon case, 
%the interpolant is $\G_r(s)$, which is a function of $\HH_r(s)$, and the interpolated function is $\G(s)$, which is a function of $\HH(s)$; thus $\HH_r(s)$ does not interpolate $\HH(s)$ in this case. However, the optimal interpolation points  and directions are still determined by the reduced model $\HH_r(s)$. The algorithmic implications of this result will be revisited in Section \ref{sec:discuss}.}
%\end{remark}
%
%
%%Proposition 
%{\color{blue}
%The following proposition sheds some light on the physical interpretation of 
%\begin{Proposition}
%Let  $\G(s)=-e^{-s{\tf}}\C(s\I-\A)^{-1}e^{\A {\tf}}\B+\HH(s)$ where $\HH(s)=\C(s\I-\A)^{-1}\B$  is the transfer function of \eqref{fom1}. Then, $\norm{\G}_{\ch_2({\tf})}=\norm{\HH}_{\ch_2({\tf})}$
%\end{Proposition}
%\begin{pf}
%Note 
%\begin{align*}
%\G(s)&=-e^{-s{\tf}}\C(s\I-\A)^{-1}e^{\A {\tf}}\B+\HH(s)\\
%&=-e^{-s{\tf}}\sum_{i=1}^n \dfrac{\phi_i e^{\lambda_i {\tf}}}{s-\lambda_i}+\HH(s)
%\end{align*}
%where $\lambda_i$-s and $\phi_i$-s are the poles and the residues of the system, respectively. 
%Consider the inverse Laplace transform of $\G(s)$:
%\begin{align*}
%\mathcal{L}^{-1}\{\G(s)\}&=\h(t)+\sum_{i=1}^n u_{\tf}(t)\phi_i e^{\lambda_i {\tf}}e^{\lambda_i (t-{\tf})}\\
%&=\h(t)+\sum_{i=1}^n u_{\tf}(t)\phi_i e^{\lambda_i t}
%\end{align*}
%where $u_{\tf}(t)$ is the unit step function
%\begin{align*}
%u_{\tf}(t)=
% \begin{cases} 
%      1 &    t\leq {\tf} \\    
%      0 &    t > {\tf} 
%   \end{cases}.
%\end{align*}
%Thus, 
%\begin{align*}
%\norm{\G}_{\ch_2({\tf})}&=\int_0^{\tf}\h(t)+\sum_{i=1}^n u_{\tf}(t)\phi_i e^{\lambda_i t} dt\\
%&=\int_0^{\tf}\h(t)dt\\
%&=\norm{\HH}_{\ch_2({\tf})}
%\end{align*}
%\end{pf}
%This proposition and its proof suggest that we are matching the models up to $t_f$. For $t>t_f$, we treat the model as insignificant, and the impulse response vanishes after $t_f$.
%}
%

@@

   For the ISS model (Figure \ref{fig:iss}), we use  TLBT and \goyal \ initializations since  POD approximations was very poor and  is excluded. In this case, we reduce the order from $r=2$ to $r=14$ with increments of $2$. For the unstable model (Figure \ref{fig:uns}), we use POD and \goyal \ initializations; for this model our implementation of TLBT produced  poor results and is avoided. In this case,  we reduce the order from $r=2$ to $r=12$ with increments of $2$.  
 The first observation is that,  since  \FH \ is a descent-method and drives the initialization to a local minimizer,  it improves the accuracy of  the reduced model for all three initializations as expected. The improvements could be dramatic. For example, 
 \FH \ is able to outperform POD as much as by an order of magnitude, see, for example,
 Figure \ref{fig:hm}, the  $r=4$ and $r=5$ cases. 
 While \FH \ improves TLBT and \goyal\ initialization as well, the improvements for the heat model are not as significant. However, for the ISS model,
\FH \ is able to improve the TLBT performance as much as $50\%$; see, e.g., Figure \ref{fig:iss}, the $r=8$ case. 
The best improvement of the \goyal \ initialization has occurred for the unstable model. For example, for $r=8$, for the unstable model, \FH\ improved the reduced model by more than $40 \%$. Gains were significantly better for POD, especially for larger $r$ values. 
{\color{blue} 
}

@@

 \begin{figure}[H]
 \centering
  \includegraphics [scale=0.35]{fig2i}
 \caption{\FH \ and other algorithms for the heat model \label{fig:iss}}
 \end{figure}
  \begin{figure}[H]
 \centering
   \includegraphics [scale=0.35]{fig3u}
      \caption{\FH \ and other algorithms for the unstable model \label{fig:uns}}
 \end{figure}

\textcolor{blue}{Finally, in Figure \ref{fig:impulse}, we compare the error in the impulse responses due to POD and \FH \ for the ISS model. For both methods, POD and \FH\  the reduced model was of order $r=14$. As we can see from the graph, \FH \ clearly outperforms POD on the time interval $[0, 1]$.}

 \begin{figure}[H]
 \centering
   \includegraphics [scale=0.35]{ISS1RErrorSmooth}
      \caption{\FH \ and POD for the ISS 1R model \label{fig:impulse}}
 \end{figure}

>>>>

%\documentclass[twocolumn][preprint]{elsarticle}
\documentclass[twocolumn]{autart}  
\input{paperPreamble}

@@

\end{frontmatter}
%Introduction
%Introduction
\section{Introduction}
%Simulation, design, and control of dynamical systems play an important role in numerous scientific and industrial tasks such as signal propagation in the nervous system\cite{kellems2009low}, heat dissipation, prediction of major weather events \cite{BoyP11,Sha03,Ant05}. 
Simulation, design, and control of dynamical systems play an important role in numerous scientific and industrial tasks such as \textcolor{black}{signal propagation in the nervous system\cite{kellems2009low};  the synthesis  of
interconnect \cite{BonD07} and semiconductor devices \cite{Hess2014}; large-scale inverse problems,
 \cite{Druskin2011solution,Lieberman2010,de2015nonlinear}; and prediction of major weather events \cite{Ant05}.}
The need for  detailed  models due to the increasing demand for greater resolution leads to  
large-scale dynamical systems, posing tremendous computational difficulties when applied in numerical simulations. In order to overcome these challenges, we perform  model reduction where we replace the large-scale dynamics with high-fidelity reduced representations.

@@

\textcolor{black}{In this paper,  we explore optimal model reduction over a finite time horizon. We use a time-limited version of the $\ch_2$ norm, denoted by $\ch_2(\tf)$, to quantify the model reduction error.}
 Optimality requires a parametrization of the reduced model. We will work with the time-domain representation of the dynamical system to derive the optimality conditions. Specifically, we represent the impulse response of the reduced dynamical system using the modal decomposition, i.e.,
 \begin{equation}\label{kernel}
\begin{aligned}
\h_r(t)=\C_r e^{\A_r t}\B_r=\sum_{i=1}^r e^{\lambda_it}\lc_i\rc_i^T.
\end{aligned}
\end{equation}
where $\lambda_i$'s are the eigenvalues of $\A_r$, and $\lc_i \in \CC^{p\times 1}, \rc_i\in \CC^{m\times1}$. 
In other words, the impulse response is expressed as a sum of $r$ rank-1 $p\times m$  matrices.
To simplify the presentation,  we assume  that $\lambda_i$'s, the reduced order poles,  are simple.  The representation \eqref{kernel} 
is nothing but a state-space transformation on $\h_r(t)=\C_r e^{\A_r t}\B_r$ using the eigenvectors of $\A_r$. 
Using the parametrization of the reduced model in \eqref{kernel}, we derive interpolatory optimality conditions in the $\ch_2(\tf)$ norm and implement a model reduction algorithm that satisfies these optimality conditions.

\textcolor{black}{The advantage of the interpolation framework we will develop  is that 
we do not require the reduced-model to be obtained via projection, as usually assumed in model reduction \cite{Ant05}. Indeed, one observation we will make is that unlike in the infinite-horizon $\ch_2$ approximation problem, the optimal reduced model in the finite-horizon case is not necessarily given by a projection and thus a projection-based approach will not be able to satisfy the optimality conditions. Therefore,  
by treating the poles and residues in \eqref{kernel} as the parameters and directly working with them, we  obtain a reduced model to satisfy the optimality conditions exactly.}

@@

%Interpolatory Model Reduction
\subsection{Interpolatory Conditions for Optimal $\ch_2$ Model Reduction}
Given a reduced order $r$, the goal is to construct a reduced order model whose transfer function $\HH_r(s)$ minimizes the $\ch_2$ error norm $\norm{\HH - \HH_r}_{\ch_2}$.  Since this is a non-convex optimization problem, the usual, numerically feasible, approach  is to find a reduced model that satisfies the necessary conditions for $\ch_2$ optimality. These conditions can be formulated in terms of Sylvester equations \cite{Wil70,HylB85} or interpolation \cite{MeiL67,GugBA08}. These two frameworks are equivalent \cite{GugBA08}. In this paper, we will focus on the interpolation framework.
\begin{theorem} \label{h2thm}%{\text{\cite {MeiL67, GugBA08}}}
Let 
$$
\h_r(t)=\sum_{k=1}^r e^{\lambda_kt}\lc_k\rc_k^T \qquad \Longleftrightarrow \qquad \HH_r(s) = \sum_{k=1}^r \frac{\lc_k\rc_k^T}{s-\lambda_k}
$$
be the best $r^{th}$ order approximation of an asymptotically stable linear dynamical system  $\HH(s)$ with respect to the $\ch_2$ norm. Then, for $k=1, 2, ... , r$,
\begin{equation} \label{eqn:h2cond}
\begin{aligned}
\lc_k^T\HH(-\lambda_k)&=\lc_k^T\HH_r(-\lambda_k),\\~~
\HH(-\lambda_k)\rc_k&=\HH_r(-\lambda_k)\rc_k,\\
\lc_k^T\HH'(-\lambda_k)\rc_k&=\lc_k^T\HH_r'(-\lambda_k)\rc_k,
\end{aligned}
\end{equation}

{\color{black} where $\HH'(s)$ denotes the derivative of $\HH(s)$ with respect to $s$.}
\end{theorem}
{\color{black}For more details on Theorem \ref{h2thm}, see {\cite {GugBA08,AntBG10b}}.}
This result states that the transfer function of the optimal $\ch_2$ approximation to $\HH(s)$ is a (tangential) Hermite interpolant where the interpolation points are the mirror images of the reduced-order poles $\{\lambda_k\}$, and the tangental directions are given by the corresponding residues $\{\lc_k\rc_k^T\}$.  Since the optimality conditions depend on the reduced-model to be computed, the solution requires a nonlinear iteration. The Iterative Rational Krylov Algorithm (IRKA)  \cite{GugBA08} and its variants such as \cite{beattie2012realization,gerstner2007hom,CasL18,beattie2009trust} use these interpolation based optimality conditions to produce   an interpolatory, locally $\ch_2$ optimal reduced model. The next section will extend this framework to the finite-time interval case.

%FH model reduction
\section{$\ch_2(\tf)$ Optimal Model Reduction on a Finite Horizon}  \label{sec:main} 
%If we are interested  in the behavior of a system only in a finite time interval (or access to a numerical simulation only on a finite time interval), we can obtain better reduced models by defining the measure of approximation quality over the interval of interest, instead of  focussing on the infinite time horizon. 
%
{\color{black}
In this section, we present  the main theoretical results of the paper i.e., the interpolatory $\ch_2(\tf)$  optimality conditions, and discuss their implications.}

@@

%Error measures in a finite-time horizon
\subsection{$\ch_2(t_f)$ Norm on a Finite-time Horizon}
It is immediately clear from the time-domain definition of the (infinite-horizon) $\ch_2$ norm how to define the finite-horizon version:
\begin{Definition}\label{innerh2}
Let $\h(t)$ and $\g(t)$ denote the impulse responses of two dynamical systems with real state-space realizations.  
For a finite-time horizon 
$[0,t_f]$, the $\ch_2(\tf)$\footnote{\textcolor{black}{Even though the term  $\ch_2$ is mostly associated with a measure in the frequency domain, following \cite{RedK17,GoyR17} we are using the notation $\ch_2(\tf)$ here as well to denote the error measure specifically formulated in the time domain. Our main reason is to keep the connection to the infinite horizon problem where the measure in the frequency- and time-domains are equivalent. And more importantly, as in the regular $\ch_2$ case, the optimality conditions will still appear as interpolation conditions in the frequency domain. 
 %In the Since the time domain and frequency domain functions are equivalent,  this notation is appropriate. Furthermore, since the infinite horizon, and finite horizon case appear to be connected, the notation $\mathcal{H}_2(t_f)$ illustrates this connection. \cite{RedK17,GoyR17} use similar notation.
 }}
   inner product $\langle \cdot, \cdot \rangle_{\ch_2(\tf)}$ 
and $\ch_2(\tf)$ norm $\norm{\cdot}_{\ch_2(\tf)}$ are defined as  
\begin{align*}
\langle \h, \g \rangle_{\ch_2(\tf)} &=\int_0^{\tf} \mathsf{Tr}( (\h(t))^T \g(t)) dt, \\%\quad \mbox{and}\quad
\norm{\h}_{\ch_2(\tf)} &=\sqrt{\int_0^{\tf} \norm{\h(t)}_F^2 dt}.
\end{align*}

@@

{\color{black}

@@

%\begin{dmath}\label{eqn:l1} 
%\pder[\J]{\lambda_k} =-2\lc_k^T \left(\sum_{j=1}^n \cc_j\bb_j^T \dfrac{({\tf}(\lambda_k+\rho_j)-1)e^{(\rho_j+\lambda_k){\tf}}+1}{(\lambda_k+\rho_j)^2}\right)\rc_k  
%+2\lc_k^T \left(\sum^r_{i=1} \lc_i\rc_i^T\dfrac{({\tf}(\lambda_i+\lambda_j\k)-1)e^{(\lambda_i+\lambda_k){\tf}}+1}{(\lambda_i+\lambda_k)^2}\right)\rc_k.
%\end{dmath}
%\end{aligned}
%\end{equation}
Lemma \eqref{mgexp}, specifically \eqref{eqn:Gpatlk} and \eqref{eqn:Grpatlk}, show that the expressions in the parentheses in \eqref{eqn:l11}  and \eqref{eqn:l12}   are, respectively, $-\G'(-\lambda_k)$ and $-\G_r'(-\lambda_k)$.
If $\pder[\J]{\lambda_k}= 0$, then
\begin{align*}
\lc_k^T\G'(-\lambda_k)\rc_k&=\lc_k^T\G_r'(-\lambda_k)\rc_k,
\end{align*}
which completes the proof.
\begin{flushright} $\Box$  \end{flushright}
{\color{black} We note that the interval of interest is problem dependent and the choice of the interval, i.e., the choice of $t_f$, may depend on the model. However, these optimality conditions hold for any choice of $t_f>0$.}

%Remark
\begin{remark}
{\color{black} In the infinite-horizon case, if  $\HH_r(s)$ is the best $\ch_2$ approximation to $\HH(s)$, then $\HH_r(s)$ interpolates $\HH(s)$. However, in the finite-horizon case, 
the interpolant is $\G_r(s)$, and the interpolated function is $\G(s)$; thus $\HH_r(s)$ does not interpolate $\HH(s)$. To give more intuition about these resulting interpolation conditions, consider the time-limited function $\g(t)$ such that 
$\g(t)=\h(t)$ when   $t\leq {\tf}$ and $\g(t)=0$ when $t > {\tf}$.
%\begin{align*}
%\g(t)=
% \begin{cases} 
%      \h(t) &    t\leq {\tf}, \\    
%      0 &    t > {\tf}.
%   \end{cases}
%\end{align*}
A direct calculation shows that $\G(s)$ is the Laplace transform of $\g(t)$. Similarly let $\g_r(t)$ 
denote the time-limited version of $\h_r(t)$. Then its Laplace transform is 
 $\G_r(s)$.  Therefore, the optimality conditions  \eqref{eqn:cond1}--\eqref{eqn:cond3}
 correspond to optimal interpolation of $\G(s)$ (Laplace transform of the time-limited function
 $\g(t)$)
 by $\G_r(s)$ (Laplace transform of the time limited function  $\g_r(t)$). The fact that  
 $\g(t)$ and   $\g_r(t)$ are both time-limited is the precise reason  why we cannot simply apply $\ch_2$ optimal reduction  to $\G(s)$. The method of \cite{beattie2012realization}, called TF-IRKA, does not require the original function to be a rational function. Thus, in principle we can use TF-IRKA to reduce $\G(s)$. However, the resulting reduced model is a rational function without any structure. In our case, the reduced model $\G_r(s)$ needs to retain the same structure as $\G(s)$ so that we can extract an $\HH_r(s)$. In other words, if we simply apply an $\ch_2$ optimal algorithm to $\G(s)$, we would be approximating a finite horizon model by an infinite horizon one and we cannot extract $\HH_r(s)$. Therefore, a new  algorithmic framework  is needed as we discuss in more detail in Section \ref{sec:discuss}.}
\end{remark}

\begin{remark}
{\color{black}
For an unstable dynamical system without any purely imaginary eigenvalues, one can work with the
 $\mathcal{L}_2$ norm by decomposing it into a stable and anti-stable system, and then obtain an interpolatory reduced model based on this measure.  However, this solution requires destroying the causality of the underlying dynamics \cite{magruder2010rational}. This is not the framework we are interested in here and we  work with a finite-time interval. }
 \end{remark}

%%remark
%\begin{remark}
%{\color{black} In the infinite-horizon case, if $\HH_r(s)$ is the best $\ch_2$ approximation to $\HH(s)$, then $\HH_r(s)$ interpolates $\HH(s)$. However, in the finite-horizon case, 
%the interpolant is $\G_r(s)$, which is a function of $\HH_r(s)$, and the interpolated function is $\G(s)$, which is a function of $\HH(s)$; thus $\HH_r(s)$ does not interpolate $\HH(s)$ in this case. However, the optimal interpolation points  and directions are still determined by the reduced model $\HH_r(s)$. The algorithmic implications of this result will be revisited in Section \ref{sec:discuss}.}
%\end{remark}
%
%
%%Proposition 
%{\color{black}
%The following proposition sheds some light on the physical interpretation of 
%\begin{Proposition}
%Let  $\G(s)=-e^{-s{\tf}}\C(s\I-\A)^{-1}e^{\A {\tf}}\B+\HH(s)$ where $\HH(s)=\C(s\I-\A)^{-1}\B$  is the transfer function of \eqref{fom1}. Then, $\norm{\G}_{\ch_2({\tf})}=\norm{\HH}_{\ch_2({\tf})}$
%\end{Proposition}
%\begin{pf}
%Note 
%\begin{align*}
%\G(s)&=-e^{-s{\tf}}\C(s\I-\A)^{-1}e^{\A {\tf}}\B+\HH(s)\\
%&=-e^{-s{\tf}}\sum_{i=1}^n \dfrac{\phi_i e^{\lambda_i {\tf}}}{s-\lambda_i}+\HH(s)
%\end{align*}
%where $\lambda_i$-s and $\phi_i$-s are the poles and the residues of the system, respectively. 
%Consider the inverse Laplace transform of $\G(s)$:
%\begin{align*}
%\mathcal{L}^{-1}\{\G(s)\}&=\h(t)+\sum_{i=1}^n u_{\tf}(t)\phi_i e^{\lambda_i {\tf}}e^{\lambda_i (t-{\tf})}\\
%&=\h(t)+\sum_{i=1}^n u_{\tf}(t)\phi_i e^{\lambda_i t}
%\end{align*}
%where $u_{\tf}(t)$ is the unit step function
%\begin{align*}
%u_{\tf}(t)=
% \begin{cases} 
%      1 &    t\leq {\tf} \\    
%      0 &    t > {\tf} 
%   \end{cases}.
%\end{align*}
%Thus, 
%\begin{align*}
%\norm{\G}_{\ch_2({\tf})}&=\int_0^{\tf}\h(t)+\sum_{i=1}^n u_{\tf}(t)\phi_i e^{\lambda_i t} dt\\
%&=\int_0^{\tf}\h(t)dt\\
%&=\norm{\HH}_{\ch_2({\tf})}
%\end{align*}
%\end{pf}
%This proposition and its proof suggest that we are matching the models up to $t_f$. For $t>t_f$, we treat the model as insignificant, and the impulse response vanishes after $t_f$.
%}
%

@@

   For the ISS model (Figure \ref{fig:iss}), we use  TLBT and \goyal \ initializations since  POD approximations was very poor and  is excluded. In this case, we reduce the order from $r=2$ to $r=14$ with increments of $2$. For the unstable model (Figure \ref{fig:uns}), we use POD and \goyal \ initializations; for this model our implementation of TLBT produced  poor results and is avoided. In this case,  we reduce the order from $r=2$ to $r=12$ with increments of $2$.  
 The first observation is that,  since  \FH \ is a descent-method and drives the initialization to a local minimizer,  it improves the accuracy of  the reduced model for all three initializations as expected. The improvements could be dramatic. For example, 
 \FH \ is able to outperform POD as much as by an order of magnitude, see, for example,
 Figure \ref{fig:hm}, the  $r=4$ and $r=5$ cases. 
 While \FH \ improves TLBT and \goyal\ initialization as well, the improvements for the heat model are not as significant. However, for the ISS model,
\FH \ is able to improve the TLBT performance as much as $50\%$; see, e.g., Figure \ref{fig:iss}, the $r=8$ case. 
The best improvement of the \goyal \ initialization has occurred for the unstable model. For example, for $r=8$, for the unstable model, \FH\ improved the reduced model by more than $40 \%$. Gains were significantly better for POD, especially for larger $r$ values. 
{\color{black} 
}

@@

 \begin{figure}[H]
 \centering
  \includegraphics [scale=0.35]{fig2i}
 \caption{\FH \ and other algorithms for the ISS model \label{fig:iss}}
 \end{figure}
  \begin{figure}[H]
 \centering
   \includegraphics [scale=0.35]{fig3u}
      \caption{\FH \ and other algorithms for the unstable model \label{fig:uns}}
 \end{figure}

\textcolor{black}{Finally, in Figure \ref{fig:impulse}, we compare the error in the impulse responses due to POD and \FH \ for the ISS model. For both methods, POD and \FH\  the reduced model was of order $r=14$. As we can see from the graph, \FH \ clearly outperforms POD on the time interval $[0, 1]$.}

 \begin{figure}[H]
 \centering
   \includegraphics [scale=0.35]{ISS1RErrorSmooth}
      \caption{\FH \ and POD for the ISS model \label{fig:impulse}}
 \end{figure}
